### 2022-05-06 paper/ase22/intro.tex
revise table3

\noindent \textbf{C1.} generating sentences with diverse syntactic
structure is challenging since text have a higher order of its
structure. However, the structures are obscured by word usage. To
address the challenge, \tool establishes specifications for evaluating
a linguistic capability and searches suitable sentences that satisfy
the specification from existing public dataset. In this process, \tool
generates new inputs by mutating the searched sentences, used as seed
inputs. \tool expands seed input grammar structures and determines its
available \pos to maintain structural naturalness.

@@

\noindent \textbf{C2.} Suitability of test case for evaluating NLP
model on a \lc is obtained from its high relevancy to the
\lc. Relevancy between test case and \lc is difficult to be measured
because the \lc is defined on a specific phenomenon appeared in the
mixture of textual structure and semantic, and understanding each test
case with respect to the phenomenon and measuring its relevancy are
not trivial. To address the difficulty, \tool implements search rules
and the transformation templates of \lcs. In addition, anlyzing parse
tree of seed sentence is used for its expansion identification.
%% \tool adopts behavioral model testing method by
%% introducing multiple behaviors from \lcs on \sa tasks and generating
%% inputs relevant to each \lc. Each test case provides not only
%% correctness of model prediction on it, but \lc on the test case also
%% gives information about classification on the model
%% performance. Therefore assigning appropriate \lc for each test case
%% alleviates overestimation of model testing results.

\noindent \textbf{C3.} Last challenge is on estimating the
appropriateness of test oracle. For \sa task, test oracle is
determined by understanding meaning from text. The meaning of text is
sensitive to its semnatic, structure, and the combination of
two. Therefore, generation of test case ought to ensure the
correctness of its oracle allocation. In this work, \tool obtain the
appropriateness of test oracle by implementing domain-specific
knowledge on word sentiment dataset and word suggestion model
pre-trained on large corpus for validation of generated sentence and
its oracle.

>>>>

\noindent \textbf{C1.} The first challenge comes with the second and
third challenges of maintaining the label and linguistic capability of
the test sentence while making the syntactic structure of the sentence
more diverse. In addition, text have a higher order of structures and
structures are obscured by word usage~\cite{}. To address the
challenge, \tool establishes specifications for evaluating a
linguistic capability and searches suitable sentences that satisfy the
specification from existing public dataset. In this process, \tool
generates new inputs by mutating the searched sentences, used as seed
inputs. \tool expands seed input grammar structures and determines its
available \pos to maintain structural naturalness.

@@

\noindent \textbf{C2.} Suitability of test sentences for evaluating
NLP model on a \lc is obtained from its high relevancy to the
\lc. Relevancy between a test sentence and its \lc is challenging to
be maintained during the transformation and expansion of the test
sentence.  This is because the \lc is defined on a specific mixture of
syntaxe and semantics of the sentence, and there exists no automatic
way to check the consistency between each sentence with the semantics
specified in corresponding \lc due to the inherent ambiguity of
natural language sentences. To address the difficulty, \tool
implements search rules and the transformation templates of \lcs. In
addition, anlyzing parse tree of seed sentence is used for its
expansion identification.
%% \tool adopts behavioral model testing method by
%% introducing multiple behaviors from \lcs on \sa tasks and generating
%% inputs relevant to each \lc. Each test case provides not only
%% correctness of model prediction on it, but \lc on the test case also
%% gives information about classification on the model
%% performance. Therefore assigning appropriate \lc for each test case
%% alleviates overestimation of model testing results.

\noindent \textbf{C3.} Last challenge is on automated test oracle.
For NLP tasks, test oracle is determined by understanding meaning from
texts. This requires domain knowledge for different NLP tasks
% Therefore, generation of test case ought to ensure the
%correctness of its oracle allocation.
In this work, as a first step, we consider \sa as the NLP task for the
models under test. \tool obtain the appropriateness of test oracle by
implementing domain-specific knowledge on word sentiment dataset and
word suggestion model pre-trained on large corpus for validation of
generated sentence and its oracle.

### 2022-05-06 paper/ase22/result.tex
revise table3

>>>>

\jl{The following needs to be in RQ2 result section after simin
  completes RQ2 result section} Table~\ref{table:TestResult} shows
results of evaluation of three \sa models. First column lists
linguistic capability for \sa task, and Columns 2-3 show the number of
seed and expanded test cases respectively. Columns 4-5 show the
failure rate in percentage by running the \sa models on the seed and
expanded test cases respectively. Column 6 shows the number of
expanded test cases failed, but their seed test cases passed. For LC9,
we combine two

From the
table, we can observe that

### 2022-05-06 paper/ase22/tables/test-results-numbers.tex
revise table3

\DefMacro{test-results-lc0}{Author sentiment is more important than of others}
\DefMacro{test-results-bl-lc0-num-sents}{8528}
\DefMacro{test-results-bl-model0-lc0-num-fail}{3741}
\DefMacro{test-results-lc1}{Negated negative should be positive or neutral}
\DefMacro{test-results-bl-lc1-num-sents}{6786}
\DefMacro{test-results-bl-model0-lc1-num-fail}{799}
\DefMacro{test-results-lc2}{Negated neutral should still be neutral}
\DefMacro{test-results-bl-lc2-num-sents}{2496}
\DefMacro{test-results-bl-model0-lc2-num-fail}{2427}
\DefMacro{test-results-lc3}{Negated positive with neutral content in the middle}
\DefMacro{test-results-bl-lc3-num-sents}{1000}
\DefMacro{test-results-bl-model0-lc3-num-fail}{860}
\DefMacro{test-results-lc4}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-bl-lc4-num-sents}{2124}
\DefMacro{test-results-bl-model0-lc4-num-fail}{1871}
\DefMacro{test-results-lc5}{Sentiment change over time, present should prevail}
\DefMacro{test-results-bl-lc5-num-sents}{8000}
\DefMacro{test-results-bl-model0-lc5-num-fail}{1680}
\DefMacro{test-results-lc6}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-bl-lc6-num-sents}{1716}
\DefMacro{test-results-bl-model0-lc6-num-fail}{1330}
\DefMacro{test-results-lc7}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-bl-lc7-num-sents}{8658}
\DefMacro{test-results-bl-model0-lc7-num-fail}{26}
\DefMacro{test-results-lc8}{Parsing positive and negative sentiment in (question, no) form}
\DefMacro{test-results-bl-lc8-num-sents}{7644}
\DefMacro{test-results-bl-model0-lc8-num-fail}{4056}
\DefMacro{test-results-lc9}{parsing sentiment in (question, yes) form}
\DefMacro{test-results-bl-lc9-num-sents}{9204}
\DefMacro{test-results-bl-model0-lc9-num-fail}{1793}
\DefMacro{test-results-bl-model1-lc0-num-fail}{2692}
\DefMacro{test-results-bl-model1-lc1-num-fail}{218}
\DefMacro{test-results-bl-model1-lc2-num-fail}{2304}
\DefMacro{test-results-bl-model1-lc3-num-fail}{416}
\DefMacro{test-results-bl-model1-lc4-num-fail}{445}
\DefMacro{test-results-bl-model1-lc5-num-fail}{829}
\DefMacro{test-results-bl-model1-lc6-num-fail}{1391}
\DefMacro{test-results-bl-model1-lc7-num-fail}{139}
\DefMacro{test-results-bl-model1-lc8-num-fail}{4576}
\DefMacro{test-results-bl-model1-lc9-num-fail}{1262}
\DefMacro{test-results-bl-model2-lc0-num-fail}{3535}
\DefMacro{test-results-bl-model2-lc1-num-fail}{734}
\DefMacro{test-results-bl-model2-lc2-num-fail}{2450}
\DefMacro{test-results-bl-model2-lc3-num-fail}{865}
\DefMacro{test-results-bl-model2-lc4-num-fail}{2124}
\DefMacro{test-results-bl-model2-lc5-num-fail}{2532}
\DefMacro{test-results-bl-model2-lc6-num-fail}{1661}
\DefMacro{test-results-bl-model2-lc7-num-fail}{125}
\DefMacro{test-results-bl-model2-lc8-num-fail}{6440}
\DefMacro{test-results-bl-model2-lc9-num-fail}{1557}
\DefMacro{test-results-lc0-num-seeds}{50}
\DefMacro{test-results-lc0-num-exps}{2323}
\DefMacro{test-results-model0-lc0-num-seed-fail}{22}
\DefMacro{test-results-model0-lc0-num-exp-fail}{1163}
\DefMacro{test-results-model0-lc0-num-pass-to-fail}{134}

@@

\DefMacro{test-results-lc1-num-exps}{1784}
\DefMacro{test-results-model0-lc1-num-seed-fail}{46}
\DefMacro{test-results-model0-lc1-num-exp-fail}{1680}
\DefMacro{test-results-model0-lc1-num-pass-to-fail}{49}
\DefMacro{test-results-lc2-num-seeds}{26}
\DefMacro{test-results-lc2-num-exps}{1009}
\DefMacro{test-results-model0-lc2-num-seed-fail}{24}
\DefMacro{test-results-model0-lc2-num-exp-fail}{932}
\DefMacro{test-results-model0-lc2-num-pass-to-fail}{62}
\DefMacro{test-results-lc3-num-exps}{1634}
\DefMacro{test-results-model0-lc3-num-seed-fail}{42}
\DefMacro{test-results-model0-lc3-num-exp-fail}{1438}
\DefMacro{test-results-model0-lc3-num-pass-to-fail}{40}
\DefMacro{test-results-lc4-num-seeds}{50}
\DefMacro{test-results-lc4-num-exps}{1486}
\DefMacro{test-results-model0-lc4-num-seed-fail}{50}
\DefMacro{test-results-model0-lc4-num-exp-fail}{1486}
\DefMacro{test-results-model0-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-lc8-num-seeds}{100}
\DefMacro{test-results-lc8-num-exps}{2379}
\DefMacro{test-results-model0-lc8-num-seed-fail}{71}
\DefMacro{test-results-model0-lc8-num-exp-fail}{1723}
\DefMacro{test-results-model0-lc8-num-pass-to-fail}{40}
\DefMacro{test-results-lc5-num-exps}{-}
\DefMacro{test-results-model0-lc5-num-seed-fail}{12}
\DefMacro{test-results-model0-lc5-num-exp-fail}{-}
\DefMacro{test-results-model0-lc5-num-pass-to-fail}{-}
\DefMacro{test-results-lc6-num-seeds}{19}
\DefMacro{test-results-lc6-num-exps}{210}
\DefMacro{test-results-model0-lc6-num-seed-fail}{15}
\DefMacro{test-results-model0-lc6-num-exp-fail}{182}
\DefMacro{test-results-model0-lc6-num-pass-to-fail}{19}
\DefMacro{test-results-lc7-num-exps}{394}
\DefMacro{test-results-model0-lc7-num-seed-fail}{2}
\DefMacro{test-results-model0-lc7-num-exp-fail}{17}
\DefMacro{test-results-model0-lc7-num-pass-to-fail}{4}
\DefMacro{test-results-lc9-num-seeds}{50}
\DefMacro{test-results-lc9-num-exps}{1373}
\DefMacro{test-results-model0-lc9-num-seed-fail}{2}
\DefMacro{test-results-model0-lc9-num-exp-fail}{37}
\DefMacro{test-results-model0-lc9-num-pass-to-fail}{43}
\DefMacro{test-results-model1-lc0-num-seed-fail}{13}
\DefMacro{test-results-model1-lc0-num-exp-fail}{725}
\DefMacro{test-results-model1-lc0-num-pass-to-fail}{78}
\DefMacro{test-results-model1-lc1-num-seed-fail}{41}
\DefMacro{test-results-model1-lc1-num-exp-fail}{1537}
\DefMacro{test-results-model1-lc1-num-pass-to-fail}{64}
\DefMacro{test-results-model1-lc2-num-seed-fail}{24}
\DefMacro{test-results-model1-lc2-num-exp-fail}{939}
\DefMacro{test-results-model1-lc2-num-pass-to-fail}{38}
\DefMacro{test-results-model1-lc3-num-seed-fail}{21}
\DefMacro{test-results-model1-lc3-num-exp-fail}{664}
\DefMacro{test-results-model1-lc3-num-pass-to-fail}{54}
\DefMacro{test-results-model1-lc4-num-seed-fail}{50}
\DefMacro{test-results-model1-lc4-num-exp-fail}{1486}
\DefMacro{test-results-model1-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-model1-lc8-num-seed-fail}{79}
\DefMacro{test-results-model1-lc8-num-exp-fail}{1947}
\DefMacro{test-results-model1-lc8-num-pass-to-fail}{18}
\DefMacro{test-results-model1-lc5-num-seed-fail}{28}
\DefMacro{test-results-model1-lc5-num-exp-fail}{-}
\DefMacro{test-results-model1-lc5-num-pass-to-fail}{-}
\DefMacro{test-results-model1-lc6-num-seed-fail}{17}
\DefMacro{test-results-model1-lc6-num-exp-fail}{160}
\DefMacro{test-results-model1-lc6-num-pass-to-fail}{9}
\DefMacro{test-results-model1-lc7-num-seed-fail}{2}
\DefMacro{test-results-model1-lc7-num-exp-fail}{19}
\DefMacro{test-results-model1-lc7-num-pass-to-fail}{5}
\DefMacro{test-results-model1-lc9-num-seed-fail}{1}
\DefMacro{test-results-model1-lc9-num-exp-fail}{57}
\DefMacro{test-results-model1-lc9-num-pass-to-fail}{46}
\DefMacro{test-results-model2-lc0-num-seed-fail}{20}
\DefMacro{test-results-model2-lc0-num-exp-fail}{1040}
\DefMacro{test-results-model2-lc0-num-pass-to-fail}{31}
\DefMacro{test-results-model2-lc1-num-seed-fail}{44}
\DefMacro{test-results-model2-lc1-num-exp-fail}{1579}
\DefMacro{test-results-model2-lc1-num-pass-to-fail}{26}
\DefMacro{test-results-model2-lc2-num-seed-fail}{24}
\DefMacro{test-results-model2-lc2-num-exp-fail}{961}
\DefMacro{test-results-model2-lc2-num-pass-to-fail}{74}
\DefMacro{test-results-model2-lc3-num-seed-fail}{38}
\DefMacro{test-results-model2-lc3-num-exp-fail}{1280}
\DefMacro{test-results-model2-lc3-num-pass-to-fail}{9}
\DefMacro{test-results-model2-lc4-num-seed-fail}{50}
\DefMacro{test-results-model2-lc4-num-exp-fail}{1486}
\DefMacro{test-results-model2-lc4-num-pass-to-fail}{0}
\DefMacro{test-results-model2-lc8-num-seed-fail}{93}
\DefMacro{test-results-model2-lc8-num-exp-fail}{2216}
\DefMacro{test-results-model2-lc8-num-pass-to-fail}{12}
\DefMacro{test-results-model2-lc5-num-seed-fail}{39}
\DefMacro{test-results-model2-lc5-num-exp-fail}{-}
\DefMacro{test-results-model2-lc5-num-pass-to-fail}{-}
\DefMacro{test-results-model2-lc6-num-seed-fail}{19}
\DefMacro{test-results-model2-lc6-num-exp-fail}{198}
\DefMacro{test-results-model2-lc6-num-pass-to-fail}{0}
\DefMacro{test-results-model2-lc7-num-seed-fail}{1}
\DefMacro{test-results-model2-lc7-num-exp-fail}{11}
\DefMacro{test-results-model2-lc7-num-pass-to-fail}{8}
\DefMacro{test-results-model2-lc9-num-seed-fail}{3}
\DefMacro{test-results-model2-lc9-num-exp-fail}{76}
\DefMacro{test-results-model2-lc9-num-pass-to-fail}{14}

>>>>

\DefMacro{test-results-lc7}{Author sentiment is more important than of others}
\DefMacro{test-results-bl-lc7-num-sents}{8528}
\DefMacro{test-results-bl-model0-lc7-num-fail}{43.87}
\DefMacro{test-results-lc3}{Negated negative should be positive or neutral}
\DefMacro{test-results-bl-lc3-num-sents}{6786}
\DefMacro{test-results-bl-model0-lc3-num-fail}{11.77}
\DefMacro{test-results-lc4}{Negated neutral should still be neutral}
\DefMacro{test-results-bl-lc4-num-sents}{2496}
\DefMacro{test-results-bl-model0-lc4-num-fail}{97.24}
\DefMacro{test-results-lc6}{Negated positive with neutral content in the middle}
\DefMacro{test-results-bl-lc6-num-sents}{1000}
\DefMacro{test-results-bl-model0-lc6-num-fail}{86.00}
\DefMacro{test-results-lc5}{Negation of negative at the end, should be positive or neutral}
\DefMacro{test-results-bl-lc5-num-sents}{2124}
\DefMacro{test-results-bl-model0-lc5-num-fail}{88.09}
\DefMacro{test-results-lc2}{Sentiment change over time, present should prevail}
\DefMacro{test-results-bl-lc2-num-sents}{8000}
\DefMacro{test-results-bl-model0-lc2-num-fail}{21.00}
\DefMacro{test-results-lc0}{Short sentences with neutral adjectives and nouns}
\DefMacro{test-results-bl-lc0-num-sents}{1716}
\DefMacro{test-results-bl-model0-lc0-num-fail}{77.51}
\DefMacro{test-results-lc1}{Short sentences with sentiment-laden adjectives}
\DefMacro{test-results-bl-lc1-num-sents}{8658}
\DefMacro{test-results-bl-model0-lc1-num-fail}{0.30}
\DefMacro{test-results-lc9}{Parsing positive and negative sentiment in (question, no) form}
\DefMacro{test-results-bl-lc9-num-sents}{7644}
\DefMacro{test-results-bl-model0-lc9-num-fail}{53.06}
\DefMacro{test-results-lc8}{Parsing sentiment in (question, yes) form}
\DefMacro{test-results-bl-lc8-num-sents}{9204}
\DefMacro{test-results-bl-model0-lc8-num-fail}{19.48}
\DefMacro{test-results-bl-model1-lc7-num-fail}{31.57}
\DefMacro{test-results-bl-model1-lc3-num-fail}{3.21}
\DefMacro{test-results-bl-model1-lc4-num-fail}{92.31}
\DefMacro{test-results-bl-model1-lc6-num-fail}{41.60}
\DefMacro{test-results-bl-model1-lc5-num-fail}{20.95}
\DefMacro{test-results-bl-model1-lc2-num-fail}{10.36}
\DefMacro{test-results-bl-model1-lc0-num-fail}{81.06}
\DefMacro{test-results-bl-model1-lc1-num-fail}{1.61}
\DefMacro{test-results-bl-model1-lc9-num-fail}{59.86}
\DefMacro{test-results-bl-model1-lc8-num-fail}{13.71}
\DefMacro{test-results-bl-model2-lc7-num-fail}{41.45}
\DefMacro{test-results-bl-model2-lc3-num-fail}{10.82}
\DefMacro{test-results-bl-model2-lc4-num-fail}{98.16}
\DefMacro{test-results-bl-model2-lc6-num-fail}{86.50}
\DefMacro{test-results-bl-model2-lc5-num-fail}{100.00}
\DefMacro{test-results-bl-model2-lc2-num-fail}{31.65}
\DefMacro{test-results-bl-model2-lc0-num-fail}{96.79}
\DefMacro{test-results-bl-model2-lc1-num-fail}{1.44}
\DefMacro{test-results-bl-model2-lc9-num-fail}{84.25}
\DefMacro{test-results-bl-model2-lc8-num-fail}{16.92}
\DefMacro{test-results-lc7-num-exps}{2323}
\DefMacro{test-results-model0-lc7-num-seed-fail}{44.00}
\DefMacro{test-results-model0-lc7-num-exp-fail}{50.06}
\DefMacro{test-results-model0-lc7-num-pass-to-fail}{134}
\DefMacro{test-results-lc3-num-exps}{1784}
\DefMacro{test-results-model0-lc3-num-seed-fail}{92.00}
\DefMacro{test-results-model0-lc3-num-exp-fail}{94.17}
\DefMacro{test-results-model0-lc3-num-pass-to-fail}{49}
\DefMacro{test-results-lc4-num-seeds}{26}
\DefMacro{test-results-lc4-num-exps}{1009}
\DefMacro{test-results-model0-lc4-num-seed-fail}{92.31}
\DefMacro{test-results-model0-lc4-num-exp-fail}{92.37}
\DefMacro{test-results-model0-lc4-num-pass-to-fail}{62}
\DefMacro{test-results-lc6-num-seeds}{50}
\DefMacro{test-results-lc6-num-exps}{1634}
\DefMacro{test-results-model0-lc6-num-seed-fail}{84.00}
\DefMacro{test-results-model0-lc6-num-exp-fail}{88.00}
\DefMacro{test-results-model0-lc6-num-pass-to-fail}{40}
\DefMacro{test-results-lc5-num-exps}{1486}
\DefMacro{test-results-model0-lc5-num-seed-fail}{100.00}
\DefMacro{test-results-model0-lc5-num-exp-fail}{100.00}
\DefMacro{test-results-model0-lc5-num-pass-to-fail}{0}
\DefMacro{test-results-lc9-num-seeds}{100}
\DefMacro{test-results-lc9-num-exps}{2379}
\DefMacro{test-results-model0-lc9-num-seed-fail}{71.00}
\DefMacro{test-results-model0-lc9-num-exp-fail}{72.43}
\DefMacro{test-results-model0-lc9-num-pass-to-fail}{40}
\DefMacro{test-results-lc2-num-seeds}{50}
\DefMacro{test-results-lc2-num-exps}{-}
\DefMacro{test-results-model0-lc2-num-seed-fail}{24.00}
\DefMacro{test-results-model0-lc2-num-exp-fail}{-}
\DefMacro{test-results-model0-lc2-num-pass-to-fail}{-}
\DefMacro{test-results-lc0-num-seeds}{19}
\DefMacro{test-results-lc0-num-exps}{210}
\DefMacro{test-results-model0-lc0-num-seed-fail}{78.95}
\DefMacro{test-results-model0-lc0-num-exp-fail}{86.67}
\DefMacro{test-results-model0-lc0-num-pass-to-fail}{19}

@@

\DefMacro{test-results-lc1-num-exps}{394}
\DefMacro{test-results-model0-lc1-num-seed-fail}{4.00}
\DefMacro{test-results-model0-lc1-num-exp-fail}{4.31}
\DefMacro{test-results-model0-lc1-num-pass-to-fail}{4}
\DefMacro{test-results-lc8-num-seeds}{50}
\DefMacro{test-results-lc8-num-exps}{1373}
\DefMacro{test-results-model0-lc8-num-seed-fail}{4.00}
\DefMacro{test-results-model0-lc8-num-exp-fail}{2.69}
\DefMacro{test-results-model0-lc8-num-pass-to-fail}{43}
\DefMacro{test-results-model1-lc7-num-seed-fail}{26.00}
\DefMacro{test-results-model1-lc7-num-exp-fail}{31.21}
\DefMacro{test-results-model1-lc7-num-pass-to-fail}{78}
\DefMacro{test-results-model1-lc3-num-seed-fail}{82.00}
\DefMacro{test-results-model1-lc3-num-exp-fail}{86.15}
\DefMacro{test-results-model1-lc3-num-pass-to-fail}{64}
\DefMacro{test-results-model1-lc4-num-seed-fail}{92.31}
\DefMacro{test-results-model1-lc4-num-exp-fail}{93.06}
\DefMacro{test-results-model1-lc4-num-pass-to-fail}{38}
\DefMacro{test-results-model1-lc6-num-seed-fail}{42.00}
\DefMacro{test-results-model1-lc6-num-exp-fail}{40.64}
\DefMacro{test-results-model1-lc6-num-pass-to-fail}{54}
\DefMacro{test-results-model1-lc5-num-seed-fail}{100.00}
\DefMacro{test-results-model1-lc5-num-exp-fail}{100.00}
\DefMacro{test-results-model1-lc5-num-pass-to-fail}{0}
\DefMacro{test-results-model1-lc9-num-seed-fail}{79.00}
\DefMacro{test-results-model1-lc9-num-exp-fail}{81.84}
\DefMacro{test-results-model1-lc9-num-pass-to-fail}{18}
\DefMacro{test-results-model1-lc2-num-seed-fail}{56.00}
\DefMacro{test-results-model1-lc2-num-exp-fail}{-}
\DefMacro{test-results-model1-lc2-num-pass-to-fail}{-}
\DefMacro{test-results-model1-lc0-num-seed-fail}{89.47}
\DefMacro{test-results-model1-lc0-num-exp-fail}{76.19}
\DefMacro{test-results-model1-lc0-num-pass-to-fail}{9}
\DefMacro{test-results-model1-lc1-num-seed-fail}{4.00}
\DefMacro{test-results-model1-lc1-num-exp-fail}{4.82}
\DefMacro{test-results-model1-lc1-num-pass-to-fail}{5}
\DefMacro{test-results-model1-lc8-num-seed-fail}{2.00}
\DefMacro{test-results-model1-lc8-num-exp-fail}{4.15}
\DefMacro{test-results-model1-lc8-num-pass-to-fail}{46}
\DefMacro{test-results-model2-lc7-num-seed-fail}{40.00}
\DefMacro{test-results-model2-lc7-num-exp-fail}{44.77}
\DefMacro{test-results-model2-lc7-num-pass-to-fail}{31}
\DefMacro{test-results-model2-lc3-num-seed-fail}{88.00}
\DefMacro{test-results-model2-lc3-num-exp-fail}{88.51}
\DefMacro{test-results-model2-lc3-num-pass-to-fail}{26}
\DefMacro{test-results-model2-lc4-num-seed-fail}{92.31}
\DefMacro{test-results-model2-lc4-num-exp-fail}{95.24}
\DefMacro{test-results-model2-lc4-num-pass-to-fail}{74}
\DefMacro{test-results-model2-lc6-num-seed-fail}{76.00}
\DefMacro{test-results-model2-lc6-num-exp-fail}{78.34}
\DefMacro{test-results-model2-lc6-num-pass-to-fail}{9}
\DefMacro{test-results-model2-lc5-num-seed-fail}{100.00}
\DefMacro{test-results-model2-lc5-num-exp-fail}{100.00}
\DefMacro{test-results-model2-lc5-num-pass-to-fail}{0}
\DefMacro{test-results-model2-lc9-num-seed-fail}{93.00}
\DefMacro{test-results-model2-lc9-num-exp-fail}{93.15}
\DefMacro{test-results-model2-lc9-num-pass-to-fail}{12}
\DefMacro{test-results-model2-lc2-num-seed-fail}{78.00}
\DefMacro{test-results-model2-lc2-num-exp-fail}{-}
\DefMacro{test-results-model2-lc2-num-pass-to-fail}{-}
\DefMacro{test-results-model2-lc0-num-seed-fail}{100.00}
\DefMacro{test-results-model2-lc0-num-exp-fail}{94.29}
\DefMacro{test-results-model2-lc0-num-pass-to-fail}{0}
\DefMacro{test-results-model2-lc1-num-seed-fail}{2.00}
\DefMacro{test-results-model2-lc1-num-exp-fail}{2.79}
\DefMacro{test-results-model2-lc1-num-pass-to-fail}{8}
\DefMacro{test-results-model2-lc8-num-seed-fail}{6.00}
\DefMacro{test-results-model2-lc8-num-exp-fail}{5.54}
\DefMacro{test-results-model2-lc8-num-pass-to-fail}{14}
